TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-14 paper/draft.tex
notes

\item model narrow wavelegth region where models are good, look at specific features (\citealt{Rojas-Ayala:2012}...), or reduce resolution (\citealt{Casagrande:2008} estimated effective temperatures, bolometric luminosities, and metallicities using optical and infrared photometries) -- however we want to leverage the full wavelength range and resolution of our data.

@@

The training step consists of

@@

@@

@@

% \begin{figure}[ht]
% \begin{center}
% \includegraphics[width=16cm]{figures/derivative_jackknife_teff.png}
% \includegraphics[width=16cm]{figures/derivative_jackknife_feh.png}
% \end{center}
% \caption{Derivative plots for physical parameter model. \textit{Top:} Derivative of flux with repsect to temperature taken at the median training temperature, T$_{\rm eff}=3463K$. \textit{Bottom:} Derivative of flux with repsect to metallicity taken at the median training metallicity, [Fe/H]$=-0.03$ dex.} \label{fig:mann_derivative}
% \end{figure}

\begin{figure}[ht]
\plotone{figures/cannon_chi_dist.png}
\caption{\textit{Left:} the distribution of fits for the training sample and known samples of pre-MS stars (\citealt{Cottaar:2014}) and binary sources (\citealt{ElBadry:2018}; \citealt{Skinner:2018}); \textit{right:} the distribution of $\chi^2$ fits for all 14,827 sources in the \apogee\-\gaia\ cross match, with color cuts $1<G_{BP}-G_{RP}<6$ and $7.5<M_{G}<20$ and $\varpi>0$. We apply a quality cut of $\chi^2 < 100,000$ to the test sample for those sources we report as "safe". \label{fig:chi_dist}}
\end{figure}

>>>>

\item model narrow wavelegth region where models are good, look at specific features -- however we want to leverage the full wavelength range and resolution of our data.

@@

The \emph{training step} consists of optimizing the coefficient vector $\theta$ for fixed labels \emph{$\ell_n$} (the reference labels for a training sample): given a spectrum (a wavelength, flux, and flux uncertainty array), for \emph{N} stars and their corresponding training labels

The \emph{test step} is an inversion of the

@@

\color{gcolor}{What are all of the parameters we want to report and what do we want to emphasize? Are there other parameters (such as mass) that might be straightforward to estimate?}\color{black}

@@

JB REDO 3 CMD PLOTS SHOWING BEFORE AND AFTER SELECTION.

@@

\begin{figure}[ht]
\plotone{figures/cannon_chi_dist.png}
\caption{\textit{Left:} the distribution of fits for the training sample and known samples of pre-MS stars (\citealt{Cottaar:2014}) and binary sources (\citealt{ElBadry:2018}; \citealt{Skinner:2018}); \textit{right:} the distribution of $\chi^2$ fits for all 14,827 sources in the \apogee\-\gaia\ cross match, with color cuts $1<G_{BP}-G_{RP}<6$ and $7.5<M_{G}<20$ and $\varpi>0$. We apply a quality cut of $\chi^2 < 100,000$ to the test sample for those sources we report as ``safe''. \label{fig:chi_dist}}
\end{figure}
